Model LF

### 2022-11-07 Estimation.Rmd
Commit

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod_ds) ~ 1 + L(TSDELTALOG(prod_ds),c(1:4)) + L(TSDELTA(s_h),c(0:4)) +  L(TSDELTALOG(mean_dp_regul),c(0:4))+ L(TSDELTALOG(wage_ds),c(0:4)) +  L(TSDELTALOG(y_ds),0:4) + L(log(prod_ds),2)+  L(log(wage_ds),2)+ L(log(y_ds),2) + L(s_h,2)+ L(log(mean_dp_regul),2))

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod_ds) ~ 0 + L(TSDELTALOG(wage_ds),c(0)) +  L(TSDELTALOG(y_ds),c(0,4)) + L(log(prod_ds),2)+  L(log(wage_ds),2)+ L(log(y_ds),2) + L(log(mean_dp_regul),2))

>>>>

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod_ds) ~ 1 + L(TSDELTALOG(prod_ds),c(1:4)) + L(TSDELTA(s_h),c(0:4)) +  L(TSDELTALOG(mean_dp_regul),c(0:4))+ L(TSDELTALOG(wage_ds),c(0:4)) +  L(TSDELTALOG(y_ds),0:4) + L(log(prod_ds),1)+  L(log(wage_ds),2)+ L(log(y_ds),2) + L(s_h,2)+ L(log(mean_dp_regul),2))

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod_ds) ~ 0 + L(TSDELTALOG(wage_ds),c(0,1))  +  L(TSDELTALOG(y_ds),c(0,4)) + L(log(prod_ds),1)+  L(log(wage_ds),1)+ L(log(y_ds),1) + L(log(mean_dp_regul),2))

### 2022-11-07 max_dp endogen stød.Rmd
Commit

COMMENT> 
BEHAVIORAL> prod_ds_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_shock) = + pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_shock,2))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_8 pr_9 pr_10 pr_11
STORE> coe(222)

COMMENT> 
BEHAVIORAL> prod_ds_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_sens) = + pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_sens,2))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_8 pr_9 pr_10 pr_11
RESTRICT> pr_9 = 0.03
STORE> coe(223)

@@

```{r}
plot(((yk_ds_07b - yk_ds_bs7b) / yk_ds_bs7b), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.0011, 0.0015));
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "yellow");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("top", legend=c("All channels but productivity","Insurance rate channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","yellow","orange", "green"));
grid()
```

>>>>

COMMENT> 
BEHAVIORAL> prod_ds_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_shock) =  pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_4* TSDELTALOG(TSLAG(wage_ds,1)) +
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_shock,1))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_4 pr_8 pr_9 pr_10 pr_11
STORE> coe(222)

COMMENT> 
BEHAVIORAL> prod_ds_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_sens) =  pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_4* TSDELTALOG(TSLAG(wage_ds,1)) +
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_sens,1))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_4 pr_8 pr_9 pr_10 pr_11
RESTRICT> pr_9 = 0.03
STORE> coe(223)

@@

```{r}
plot(((yk_ds_07b - yk_ds_bs7b) / yk_ds_bs7b), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.0011, 0.0015));
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "yellow");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
lines(((yk_ds_000 - yk_ds_bs1) / yk_ds_00), col= "red");
legend("top", legend=c("All channels but productivity","Insurance rate channel", "Wage channel", "Demand channel", "LF Channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","yellow","orange", "green", "red"));
grid()
```
